---
title: "Spam or Ham message Classification"
output: html_notebook
author: "Anish Singh Walia"
---


Requiring the necessary packages-
```{r,message=FALSE,warning=FALSE}

require(quanteda)#natural language processing package
?quanteda 
require(RColorBrewer)

```

__quanteda__ makes it easy to manage texts in the form of a __corpus__, defined as a collection of texts that includes document-level variables specific to each text, as well as meta-data for documents and for the collection as a whole. quanteda includes tools to make it easy and fast to manuipulate the texts in a corpus, by performing the most common natural language processing tasks simply and quickly, such as tokenizing, stemming, or forming ngrams. quanteda’s functions for tokenizing texts and forming multiple tokenized documents into a document-feature matrix are both extremely fast and extremely simple to use. quanteda can segment texts easily by words, paragraphs, sentences, or even user-supplied delimiters and tags.

--------------


####loading the dataset


```{r}
spam<-read.csv("F:/PROJECTS/Datasets/spam.csv",header=TRUE, sep=",", quote='\"\"', stringsAsFactors=FALSE)

table(spam$v1)


#checking the distribution of type of messages
theme_set(theme_bw())
ggplot(aes(x=v1),data=spam) +
  geom_bar(fill="red",width=0.5)



```

Now let's add appropiate names to the columns.


```{r}
names(spam)<-c("type","message")
head(spam)


```

Now we can sample the data.We can randomize our data using the sample() command.If the data is not stored in a random distribution, this will help to ensure that we are dealing with a random draw from our data. The set.seed() is to ensure reproducable results.

```{r}
set.seed(2012)
spam<-spam[sample(nrow(spam)),]

```


------------------


###Now let's build the spam and ham Wordclouds

We'll use quanteda's corpus() command to construct a corpus from the Text field of our raw data.A corpus can be thought of as a master copy of our dataset from which we can pull subsets or observations as needed.

After this I will attach the Label field as a document variable to the corpus using the docvars() command. We attach Label as a variable directly to our corpus so that we can associate SMS messages with their respective ham/spam label later in the analysis.

```{r}

?corpus #to search more on this method
msg.corpus<-corpus(spam$message)
docvars(msg.corpus)<-spam$type   #ataching the label to the corpus message text

```

Let's plot the wordcloud now-

```{r}
#subsetting only the spam messages
spam.plot<-corpus_subset(msg.corpus,docvar1=="spam")

#now creating a document-feature matrix using dfm()
spam.plot<-dfm(spam.plot, tolower = TRUE, remove_punct = TRUE, remove_twitter = TRUE, remove_numbers = TRUE, remove=stopwords("SMART"))



```

