---
title: "Spam or Ham message Classification"
output: html_notebook
author: "Anish Singh Walia"
---


Requiring the necessary packages-
```{r,message=FALSE,warning=FALSE}

require(quanteda)#natural language processing package
?quanteda 
require(RColorBrewer)

```

__quanteda__ makes it easy to manage texts in the form of a __corpus__, defined as a collection of texts that includes document-level variables specific to each text, as well as meta-data for documents and for the collection as a whole. quanteda includes tools to make it easy and fast to manuipulate the texts in a corpus, by performing the most common natural language processing tasks simply and quickly, such as tokenizing, stemming, or forming ngrams. quanteda’s functions for tokenizing texts and forming multiple tokenized documents into a document-feature matrix are both extremely fast and extremely simple to use. quanteda can segment texts easily by words, paragraphs, sentences, or even user-supplied delimiters and tags.

--------------


####loading the dataset


```{r}
spam<-read.csv("F:/PROJECTS/Datasets/spam.csv",header=TRUE, sep=",", quote='\"\"', stringsAsFactors=FALSE)

table(spam$v1)


#checking the distribution of type of messages
theme_set(theme_bw())
ggplot(aes(x=v1),data=spam) +
  geom_bar(fill="red",width=0.5)



```

